---
title       : Gold Stock Prices Project
subtitle    : Shiny App Presentation
author      : Eduardo Magalhaes Barbosa
job         : Coursera Developing Data Products Projects
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
license     : by-nc-sa
github      :
  user      : EduardoMagalhaes
  repo      : SlidifyPresentation
---


## Disclaimer

1. I am an autodidact Resultado de 25 + 25 = `r 25 + 25`
2. What I present here works for me
3. Read and follow the official [Google Chart API documentation](https://developers.google.com/chart/) and [Terms of Service](https://developers.google.com/readme/terms)
4. Sometimes you have re-load this presentation for the charts and all slides to appear

---

## Agenda

* Introduction and motivation
* Google Chart Tools
* R package googleVis
  * Concepts of googleVis
  * Case studies

```{r setOptions, echo=FALSE}
options(gvis.plot.tag="chart")
```

--- .class #id 

## Motivation for googleVis

* Inspired by Hans Rosling’s talks we wanted to use interactive data visualisation tools to foster the dialogue between data analysts and others

* We wanted moving bubbles charts as well

* The software behind Hans’ talk was bought by Google and integrated as motion charts into their Visualisation API

* Ideally we wanted to use R, a language we knew

* Hence, we had to create an interface between the Google Chart Tools and R

--- 

## Introduction to Google Chart Tools

* Google Chart Tools provide a way to visualize data on web sites

* The API makes it easy to create interactive charts

* It uses JavaScript and DataTable / JSON as input

* Output is either HTML5/SVG or Flash

* Browser with internet connection required to display chart

* Please read the Google [Terms of Service](https://developers.google.com/terms/) before you start

---


## Motion chart example

```{r motionchartcode, results='asis'}
library(googleVis)
plot(gvisMotionChart(Fruits, "Fruit", "Year",
                     options=list(width=600, height=400)))
```

---


## Thanks

* Joe Cheng for code contribution to make googleVis work with shiny
* John Maindonald for reporting that the WorldBank demo didn't 
    download all data, but only the first 12000 records.
* Sebastian Campbell for reporting a typo in the Andrew and Stock
    data set and pointing out that the core charts, such as line
  charts accept also date variables for the x-axis. 
* John Maindonald for providing a simplified version of the
    WorldBank demo using the WDI package.
* John Muschelli for suggesting to add 'hovervar' as an additional
    argument to gvisGeoChart.
